---
title: "cesR Data Analysis"
author: "Shijia Yu"
date: 2020-09-25T21:13:14-05:00
bibliography: "references.bib"
categories: ["R"]
tags: ["R Markdown", "plot", "regression"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
#install.packages("tidyverse")
#install.packages("devtools")
#devtools::install_github("hodgettsp/cesR")
library(tidyverse)
library(visdat)
library(cesR)
library(skimr)
```

# Introduction

Three paragraph statement.

First paragraph: General. Motivational. Majors specific finding. 

Second paragraph: More about what you did and found.

Third paragraph: Outline of the paper. Future work. Weaknesses.
Introduce the scenario and data objective.
Type of data variable.


```{r download, warning=FALSE, message=FALSE}
# install.packages("devtools")
# devtools::install_github("hodgettsp/cesR")

cesR::get_decon()
```
# Data

The CES dataset is....

```{r}
head(decon)
```
Some initial explorations that would be used to guide this section.

```{r}
#visdat::vis_dat(decon)

#skimr::skim(decon)

#class(decon$ces_code)

decon <- 
  decon %>% 
  filter(income < 1000000)#select observations

decon <- 
  decon %>% 
  select(religion, income)#select variables
decon %>% summarise(mean_income = mean(income), sd_income = sd(income), min_income = min(income),
                    max_income = max(income), median_income = median(income))

```
The variables we focus on are....

Summary statistics for these variables...

You must include graphs.

```{r}
decon %>% 
  ggplot(aes(x = religion)) +
  geom_bar() + coord_flip()#categorical data
```

```{r}
decon %>% 
  ggplot(aes(x = income)) +
  geom_histogram()
```

```{r}
decon %>% 
  ggplot(aes(x = income)) +
  geom_histogram() +
  labs(x = "Income",
       y = "Number",
       title = "Distribution of income in 2019 CES",
       caption = "Source: Stephenson, Harell, Rubenson, Loewen, 2020.") +
  theme_bw()
```
# Discussion of the graphs

My discussion... main findings of your graph.


Features of your survey.... Non-response... etc. And how these could affect the results....

# Discussion of the Paper

## Weaknesses and next steps

My weaknesses...

# Reference
-Hadley Wickham, Jim Hester and Winston Chang (2020). devtools: Tools to Make Developing R Packages Easier.
  https://devtools.r-lib.org/, https://github.com/r-lib/devtools.
  



